---
title: "Loading data"
author: Richard J. Telford
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 1, fig.width = 5)
library("learnr")
library("tidyverse")
theme_set(theme_classic())

tutorial_options(exercise.cap = "Exercise")
```

## Data formats

This tutorial will help you to import data into R.

Data stored many different formats can be imported into R.
It is important to import the data in its original format, as converting formats may introduce errors and makes the process non-reproducible.
This tutorial uses the `readr` package for importing text files (e.g. csv files) and the `readxl` package for importing excel files

## Importing text files

The `readr` package is loaded when `tidyverse` is loaded.



The advantages of `readr` functions over base R are 


## Importing excel file

Despite well [known problems](https://doi.org/10.1186/s13059-016-1044-7) with Excel and its ease of corrupting data with it, Excel continues to be a popular format. 
Rather than exporting data from the Excel file into a `csv` file, the `readxl` package can import files directly into R.

```{r readxl}
#find names of excel sheets
readxl::excel_sheets()

readxl::read_excel()

```


### Reading multiple sheets









